---
title: "survival_probs_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{survival_probs_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Ariana)
library(survival)
```

This package takes a vector of time intervals and vector of events to calculate the survival probabilities at each interval time point. 

```{r}
time = c(1:1000)
event = sample(c(0,1), replace=TRUE, size=1000)

survival::
```

"time" should be a vector of time intervals, such as days or years, until an event of interest occurs. Typically, survival calculations are used to compare the amount of time a participant in a trial or observational study persists in the study until either death or other departure of the study, known as censoring. "event" is a vector of these events, which are recorded as a "0" (no event) or a "1" for death.

```{r}
survival <- survival.probs(time, event)

length(survival)
```

We can then view these probabilities as a curve
```{r}
plot(survival)

```

The function survival.probs() computes survival probabilities and returns a vector of these probabilities. This is the same function as a multi-step process in the survival package:
1. Compute a Surv object using a vector of time and a vector of events.
2. Use the survfit() function to compute the components of a survival curve
3. Extract the probabilities with the summary() function.
We can compare survival.probs() and summary(survfit(Surv)):
```{r}
time = c(1:6000)
event = sample(c(0,1), replace=TRUE, size=6000)

ariana_function = survival.probs(time, event)
survival_function = summary(survfit(Surv(time, event)~1))$surv

all.equal(ariana_function, survival_function)
```

